Report on a Safety Checker for Petri nets

### 2014-02-01 paper/workspace/main.tex
Changed labels of code and net

bit1 := false
while true do
  bit1 := true
  a: while bit2 do skip od
  b: <critical section>
  bit1 := false
od

@@

bit2 := false
while true do
  l: bit2 := true
  if bit1 then
    bit2 := false
    while bit1 do skip od
    goto l
  fi
  <critical section>
  bit2 := false
od

@@

\begin{center}
\begin{tikzpicture}[node distance=2cm]
  \node[place, tokens=1, label=left:a] (a) {};
  \node[place, tokens=0, label=left:b, below of=a] (b) {};
  \node[place, tokens=0, label=right:nbit2, right of=b, xshift=-1cm, yshift=+1cm] (nbit2) {};
  \node[transition, label=left:t1, above of=a, yshift=-1cm] (t1) {}
    edge [pre, bend left, min distance=2cm, out=225, in=-45] (b)
    edge [post] (a);
  \node[transition, label=left:t2] (t2) at ($(a)!0.5!(b)$) {}
    edge [pre] (a)
    edge [pre] (nbit2)
    edge [post] (b)
    edge [post] (nbit2);
\end{tikzpicture}
\end{center}

>>>>

    bit1 := false
    while true do
p1:   bit1 := true
p2:   while bit2 do skip od
p3:   <critical section>
      bit1 := false
    od

@@

    bit2 := false
    while true do
q1:   bit2 := true
q2:   if bit1 then
q3:     bit2 := false
q4:     while bit1 do skip od
        goto q1
      fi
q5:   <critical section>
      bit2 := false
od

@@

\begin{center}
\begin{tikzpicture}[node distance=2cm]
  \node[place, tokens=1, label=left:a] (a) {};
  \node[place, tokens=0, label=left:b, below of=a] (b) {};
  \node[place, tokens=0, label=right:$\neg bit2$, right of=b, xshift=-1cm, yshift=+1cm] (nbit2) {};
  \node[transition, label=left:t1, above of=a, yshift=-1cm] (t1) {}
    edge [pre, bend left, min distance=2cm, out=225, in=-45] (b)
    edge [post] (a);
  \node[transition, label=left:t2] (t2) at ($(a)!0.5!(b)$) {}
    edge [pre] (a)
    edge [pre] (nbit2)
    edge [post] (b)
    edge [post] (nbit2);
\end{tikzpicture}
\end{center}
